---
title: "Temporal communication dynamics in OSS communities: Robustness analyses"
output:
  html_document:
    keep_md: yes
    number_sections: yes
    toc: true
---

This R markdown provides the robustness analysis for our forthcoming manuscript
(Paxton, Varoquaux, Geiger, & Holdgraf, *in preparation*).

To run this from scratch, you will need the following files:

* `../../data/analysis_data/sentiment_frame_tickets-for_r.csv`: Contains cleaned
**tickets**-related data and derived variables from scraped GitHub data.
* `../../data/analysis_data/sentiment_frame_comments-for_r.csv`: Contains
cleaned **comments**-related data and derived variables from scraped GitHub
data.
* `./utils/ossc-libraries_and_functions.r`: Loads in necessary libraries and
creates new functions for our analyses.

**Code written by**: A. Paxton (University of Connecticut) & N. Varoquaux
(CNRS)

**Date last compiled**:  `r Sys.time()`

```{r silent-preparations, include=FALSE}
library(knitr)
knitr::opts_chunk$set(cache=TRUE, autodep=TRUE, cache.lazy=FALSE)
options(scipen=999)
```

***

# Preliminaries

```{r prelim, warning = FALSE, error = FALSE, message = FALSE}

# clear everything
rm(list=ls())

# load libraries and add new functions
source('./utils/ossc-libraries_and_functions.r')
source("./utils/data-loading-robustness.R")

```

***

# Create robustness datasets

Here, we'll load the data and specify two additional membership cutoffs: 
7 contributions and 10 contributions.

```{r choosing_datasets}

# specify 7-contribution cutoff
tickets_frame_7 = loading_tickets_data(dataset="original", membership_cutoff = 7)
comments_frame_7 = loading_comments_data(dataset="original", membership_cutoff = 7)

# specify 10-contribution cutoff
tickets_frame_10 = loading_tickets_data(dataset="original", membership_cutoff = 10)
comments_frame_10 = loading_comments_data(dataset="original", membership_cutoff = 10)

```

***

# Data analysis: 7-contribution cutoff

***

### Data preparation


```{r prepare-data-for-sentiment-analysis-7cutoff}

sentiment_frame_7 = combine_tickets_and_comments(tickets_frame_7, comments_frame_7)

```

### Model 1.2: Do tickets and comments materially differ in emotion over time?

#### Robustness Model 1.2: 7-contribution cutoff

```{r sentiment_modeling_per_year-7cutoff}

# create year factor
sentiment_frame_7$year = as.factor(sentiment_frame_7$year)

# specify model
timecourse_compound_emotion_7 = lmer(
  compound_emotion ~ 0 + project:type:author_group:year + (1 | author_name),
  data=sentiment_frame_7,
  REML=FALSE)

```

```{r clean-up_model-1:2c-output-7cutoff}
coefficients_and_se_7 = data.frame(
  summary(timecourse_compound_emotion_7)$coefficients)

row_names = gsub(
  "project", "", gsub(
    "author_group", "", gsub(
      "type", "", row.names(coefficients_and_se_7))))

row_names = gsub(
  "year", "", row_names)

# replace hyphens in project names with periods
row_names = gsub(
  "scikit-", "scikit.", gsub(
    "sphinx-", "sphinx.", row_names))

# convert model estimates to a dataframe
means = coefficients_and_se_7$Estimate
names(means) = row_names

# convert standard error to dataframe
se = coefficients_and_se_7$Std..Error
names(se) = row_names
```

```{r saving_results-model-1.2-7cutoff}
dir.create("results/models", showWarnings=FALSE)
write.table(coefficients_and_se_7,
            file="results/models/model-1.2-7cutoff.tsv",
            sep="\t")

```

#### Robustness Model 1.2 across projects: 7-contribution cutoff

```{r compound-emotion-all-vs-one-timecourse-7cutoff}

all_project_tests_7 = NA
all_projects = unique(sentiment_frame_7$project)

# We're going to fit the model for each projects, and concatenate the results
# in a dataframe. Then, we'll apply multiple correction and display the
# results
for(project in all_projects){
  sentiment_frame_7$test_group = sentiment_frame_7$project == project
  one_versus_all_emotion = lmer(
    compound_emotion ~ 0 + type:author_group:test_group:year + (1|author_name),
    data=sentiment_frame_7,
    REML=FALSE)
  
  # Clean up mode
  coefficients_and_se_7 = data.frame(
    summary(one_versus_all_emotion)$coefficients)
  row_names = gsub(
    "author_group", "", 
    gsub("type", "",
         gsub("project", "", row.names(coefficients_and_se_7))))
  
  means = coefficients_and_se_7$Estimate
  names(means) = row_names
  se = coefficients_and_se_7$Std..Error
  names(se) = row_names
  
  template_contrasts = c(
    "issue_post:member:test_groupTRUE-issue_post:member:test_groupFALSE",
    "pr_post:member:test_groupTRUE-pr_post:member:test_groupFALSE",
    "issue_reply:member:test_groupTRUE-issue_reply:member:test_groupFALSE",
    "pr_reply:member:test_groupTRUE-pr_reply:member:test_groupFALSE",
    "issue_post:nonmember:test_groupTRUE-issue_post:nonmember:test_groupFALSE",
    "pr_post:nonmember:test_groupTRUE-pr_post:nonmember:test_groupFALSE",
    "issue_reply:nonmember:test_groupTRUE-issue_reply:nonmember:test_groupFALSE",
    "pr_reply:nonmember:test_groupTRUE-pr_reply:nonmember:test_groupFALSE"
  )
  
  # Now, extend this to all years.
  contrasts = c(
    unlist(
      lapply(gsub("-", ":year2009-", template_contrasts),
             function(x) paste(x, ":year2009", sep=""))),
    unlist(
      lapply(gsub("-", ":year2010-", template_contrasts),
             function(x) paste(x, ":year2010", sep=""))),
    unlist(
      lapply(gsub("-", ":year2011-", template_contrasts),
             function(x) paste(x, ":year2011", sep=""))),
    unlist(
      lapply(gsub("-", ":year2012-", template_contrasts),
             function(x) paste(x, ":year2012", sep=""))),
    unlist(
      lapply(gsub("-", ":year2013-", template_contrasts),
             function(x) paste(x, ":year2013", sep=""))),
    unlist(
      lapply(gsub("-", ":year2014-", template_contrasts),
             function(x) paste(x, ":year2014", sep=""))),
    unlist(
      lapply(gsub("-", ":year2015-", template_contrasts),
             function(x) paste(x, ":year2015", sep=""))),
    unlist(
      lapply(gsub("-", ":year2016-", template_contrasts),
             function(x) paste(x, ":year2016", sep=""))),
    unlist(
      lapply(gsub("-", ":year2017-", template_contrasts),
             function(x) paste(x, ":year2017", sep=""))),
    unlist(
      lapply(gsub("-", ":year2018-", template_contrasts),
             function(x) paste(x, ":year2018", sep=""))))
  
  
  one_versus_all_emotion_tests_7 = compute_t_statistics(
    means, se,
    contrasts)
  one_versus_all_emotion_tests_7[, "p_value"] = compute_p_value_from_t_stats(
    one_versus_all_emotion_tests_7$t_stats)
  
  # Add unique identifier based on the project of interest in the table.
  row.names(one_versus_all_emotion_tests_7) = gsub(
    "test_group", project,
    row.names(one_versus_all_emotion_tests_7))
  
  if(is.null(dim(all_project_tests_7))){
    all_project_tests_7 = one_versus_all_emotion_tests_7
  }else{
    all_project_tests_7 = rbind(
      all_project_tests_7, one_versus_all_emotion_tests_7)
  }
}
```

```{r display-1.2-results-7cutoff}
all_project_tests_7 = all_project_tests_7[!is.na(all_project_tests_7[, "p_value"]), ]
pander_clean_anova(all_project_tests_7, rename_columns=FALSE,
                   display_only_significant=TRUE)
```

```{r output_timecourse_emotion_pvalues-7cutoff}
all_project_tests_7$p_val_adjusted = p.adjust(all_project_tests_7$p_value, method="BH")
write.table(all_project_tests_7,
            file="results/models/model-timecourse-emotion-pvalues-7cutoff.tsv")
```

### Model 1.4: Do tickets and comments materially differ in gratitude over time?

#### Robustness Model 1.4: 7-contribution cutoff

```{r gratitude_modeling_per_year-7cutoff}
sentiment_frame_7$year = as.factor(sentiment_frame_7$year)
timecourse_grateful_counts = lmer(
  log(grateful_count + 1) ~ 0 + project:type:author_group:year + (1 | author_name),
  data=sentiment_frame_7,
  REML=FALSE)
```

```{r clean-up_model-1:4-output-7cutoff}
coefficients_and_se_7 = data.frame(
  summary(timecourse_grateful_counts)$coefficients)

row_names = gsub(
  "project", "", gsub(
    "author_group", "", gsub(
      "type", "", row.names(coefficients_and_se_7))))

row_names = gsub(
  "year", "", row_names)

# replace hyphens in project names with periods
row_names = gsub(
  "scikit-", "scikit.", gsub(
    "sphinx-", "sphinx.", row_names))

# convert model estimates to a dataframe
means = coefficients_and_se_7$Estimate
names(means) = row_names

# convert standard error to dataframe
se = coefficients_and_se_7$Std..Error
names(se) = row_names
```

```{r saving_results-model-1.4-7cutoff}
dir.create("results/models", showWarnings=FALSE)
write.table(coefficients_and_se_7,
            file="results/models/model-1.4-7cutoff.tsv",
            sep="\t")

```

#### Robustness Model 1.4 across projects: 7-contribution cutoff

```{r grateful-counts-all-vs-one-timecourse-7cutoff}

all_project_tests_7 = NA
all_projects = unique(sentiment_frame_7$project)

# We're going to fit the model for each projects, and concatenate the results
# in a dataframe. Then, we'll apply multiple correction and display the
# results
for(project in all_projects){
  sentiment_frame_7$test_group = sentiment_frame_7$project == project
  one_versus_all_emotion = lmer(
    log(grateful_count + 1) ~ 0 + type:author_group:test_group:year + (1|author_name),
    data=sentiment_frame_7,
    REML=FALSE)
  
  # Clean up mode
  coefficients_and_se_7 = data.frame(
    summary(one_versus_all_emotion)$coefficients)
  row_names = gsub(
    "author_group", "", 
    gsub("type", "",
         gsub("project", "", row.names(coefficients_and_se_7))))
  
  means = coefficients_and_se_7$Estimate
  names(means) = row_names
  se = coefficients_and_se_7$Std..Error
  names(se) = row_names
  
  template_contrasts = c(
    "issue_post:member:test_groupTRUE-issue_post:member:test_groupFALSE",
    "pr_post:member:test_groupTRUE-pr_post:member:test_groupFALSE",
    "issue_reply:member:test_groupTRUE-issue_reply:member:test_groupFALSE",
    "pr_reply:member:test_groupTRUE-pr_reply:member:test_groupFALSE",
    "issue_post:nonmember:test_groupTRUE-issue_post:nonmember:test_groupFALSE",
    "pr_post:nonmember:test_groupTRUE-pr_post:nonmember:test_groupFALSE",
    "issue_reply:nonmember:test_groupTRUE-issue_reply:nonmember:test_groupFALSE",
    "pr_reply:nonmember:test_groupTRUE-pr_reply:nonmember:test_groupFALSE"
  )
  
  # Now, extend this to all years.
  contrasts = c(
    unlist(
      lapply(gsub("-", ":year2009-", template_contrasts),
             function(x) paste(x, ":year2009", sep=""))),
    unlist(
      lapply(gsub("-", ":year2010-", template_contrasts),
             function(x) paste(x, ":year2010", sep=""))),
    unlist(
      lapply(gsub("-", ":year2011-", template_contrasts),
             function(x) paste(x, ":year2011", sep=""))),
    unlist(
      lapply(gsub("-", ":year2012-", template_contrasts),
             function(x) paste(x, ":year2012", sep=""))),
    unlist(
      lapply(gsub("-", ":year2013-", template_contrasts),
             function(x) paste(x, ":year2013", sep=""))),
    unlist(
      lapply(gsub("-", ":year2014-", template_contrasts),
             function(x) paste(x, ":year2014", sep=""))),
    unlist(
      lapply(gsub("-", ":year2015-", template_contrasts),
             function(x) paste(x, ":year2015", sep=""))),
    unlist(
      lapply(gsub("-", ":year2016-", template_contrasts),
             function(x) paste(x, ":year2016", sep=""))),
    unlist(
      lapply(gsub("-", ":year2017-", template_contrasts),
             function(x) paste(x, ":year2017", sep=""))),
    unlist(
      lapply(gsub("-", ":year2018-", template_contrasts),
             function(x) paste(x, ":year2018", sep=""))))
  
  
  one_versus_all_emotion_tests_7 = compute_t_statistics(
    means, se,
    contrasts)
  one_versus_all_emotion_tests_7[, "p_value"] = compute_p_value_from_t_stats(
    one_versus_all_emotion_tests_7$t_stats)
  
  # Add unique identifier based on the project of interest in the table.
  row.names(one_versus_all_emotion_tests_7) = gsub(
    "test_group", project,
    row.names(one_versus_all_emotion_tests_7))
  
  if(is.null(dim(all_project_tests_7))){
    all_project_tests_7 = one_versus_all_emotion_tests_7
  }else{
    all_project_tests_7 = rbind(
      all_project_tests_7, one_versus_all_emotion_tests_7)
  }
}
```

```{r display-gratitude-results-7cutoff}
all_project_tests_7 = all_project_tests_7[!is.na(all_project_tests_7[, "p_value"]), ]
pander_clean_anova(all_project_tests_7, rename_columns=FALSE,
                   display_only_significant=TRUE)
```

```{r gratitute_write_results-7cutoff}
all_project_tests_7$p_val_adjusted = p.adjust(all_project_tests_7$p_value, method="BH")
write.table(all_project_tests_7,
            file="results/models/model-timecourse-gratitude-pvalues-7cutoff.tsv")

```

***

# Data analysis: 10-contribution cutoff

***

### Data preparation


```{r prepare-data-for-sentiment-analysis-10cutoff}

sentiment_frame_10 = combine_tickets_and_comments(tickets_frame_10, comments_frame_10)

```

### Model 1.2: Do tickets and comments materially differ in emotion over time?

#### Robustness Model 1.2: 10-contribution cutoff

```{r sentiment_modeling_per_year-10cutoff}

# create year factor
sentiment_frame_10$year = as.factor(sentiment_frame_10$year)

# specify model
timecourse_compound_emotion_10 = lmer(
  compound_emotion ~ 0 + project:type:author_group:year + (1 | author_name),
  data=sentiment_frame_10,
  REML=FALSE)

```

```{r clean-up_model-1:2c-output-10cutoff}
coefficients_and_se_10 = data.frame(
  summary(timecourse_compound_emotion_10)$coefficients)

row_names = gsub(
  "project", "", gsub(
    "author_group", "", gsub(
      "type", "", row.names(coefficients_and_se_10))))

row_names = gsub(
  "year", "", row_names)

# replace hyphens in project names with periods
row_names = gsub(
  "scikit-", "scikit.", gsub(
    "sphinx-", "sphinx.", row_names))

# convert model estimates to a dataframe
means = coefficients_and_se_10$Estimate
names(means) = row_names

# convert standard error to dataframe
se = coefficients_and_se_10$Std..Error
names(se) = row_names
```

```{r saving_results-model-1.2-10cutoff}
dir.create("results/models", showWarnings=FALSE)
write.table(coefficients_and_se_10,
            file="results/models/model-1.2-10cutoff.tsv",
            sep="\t")

```

#### Robustness Model 1.2 across projects: 10-contribution cutoff

```{r compound-emotion-all-vs-one-timecourse-10cutoff}

all_project_tests_10 = NA
all_projects = unique(sentiment_frame_10$project)

# We're going to fit the model for each projects, and concatenate the results
# in a dataframe. Then, we'll apply multiple correction and display the
# results
for(project in all_projects){
  sentiment_frame_10$test_group = sentiment_frame_10$project == project
  one_versus_all_emotion = lmer(
    compound_emotion ~ 0 + type:author_group:test_group:year + (1|author_name),
    data=sentiment_frame_10,
    REML=FALSE)
  
  # Clean up mode
  coefficients_and_se_10 = data.frame(
    summary(one_versus_all_emotion)$coefficients)
  row_names = gsub(
    "author_group", "", 
    gsub("type", "",
         gsub("project", "", row.names(coefficients_and_se_10))))
  
  means = coefficients_and_se_10$Estimate
  names(means) = row_names
  se = coefficients_and_se_10$Std..Error
  names(se) = row_names
  
  template_contrasts = c(
    "issue_post:member:test_groupTRUE-issue_post:member:test_groupFALSE",
    "pr_post:member:test_groupTRUE-pr_post:member:test_groupFALSE",
    "issue_reply:member:test_groupTRUE-issue_reply:member:test_groupFALSE",
    "pr_reply:member:test_groupTRUE-pr_reply:member:test_groupFALSE",
    "issue_post:nonmember:test_groupTRUE-issue_post:nonmember:test_groupFALSE",
    "pr_post:nonmember:test_groupTRUE-pr_post:nonmember:test_groupFALSE",
    "issue_reply:nonmember:test_groupTRUE-issue_reply:nonmember:test_groupFALSE",
    "pr_reply:nonmember:test_groupTRUE-pr_reply:nonmember:test_groupFALSE"
  )
  
  # Now, extend this to all years.
  contrasts = c(
    unlist(
      lapply(gsub("-", ":year2009-", template_contrasts),
             function(x) paste(x, ":year2009", sep=""))),
    unlist(
      lapply(gsub("-", ":year2010-", template_contrasts),
             function(x) paste(x, ":year2010", sep=""))),
    unlist(
      lapply(gsub("-", ":year2011-", template_contrasts),
             function(x) paste(x, ":year2011", sep=""))),
    unlist(
      lapply(gsub("-", ":year2012-", template_contrasts),
             function(x) paste(x, ":year2012", sep=""))),
    unlist(
      lapply(gsub("-", ":year2013-", template_contrasts),
             function(x) paste(x, ":year2013", sep=""))),
    unlist(
      lapply(gsub("-", ":year2014-", template_contrasts),
             function(x) paste(x, ":year2014", sep=""))),
    unlist(
      lapply(gsub("-", ":year2015-", template_contrasts),
             function(x) paste(x, ":year2015", sep=""))),
    unlist(
      lapply(gsub("-", ":year2016-", template_contrasts),
             function(x) paste(x, ":year2016", sep=""))),
    unlist(
      lapply(gsub("-", ":year20110-", template_contrasts),
             function(x) paste(x, ":year2017", sep=""))),
    unlist(
      lapply(gsub("-", ":year2018-", template_contrasts),
             function(x) paste(x, ":year2018", sep=""))))
  
  
  one_versus_all_emotion_tests_10 = compute_t_statistics(
    means, se,
    contrasts)
  one_versus_all_emotion_tests_10[, "p_value"] = compute_p_value_from_t_stats(
    one_versus_all_emotion_tests_10$t_stats)
  
  # Add unique identifier based on the project of interest in the table.
  row.names(one_versus_all_emotion_tests_10) = gsub(
    "test_group", project,
    row.names(one_versus_all_emotion_tests_10))
  
  if(is.null(dim(all_project_tests_10))){
    all_project_tests_10 = one_versus_all_emotion_tests_10
  }else{
    all_project_tests_10 = rbind(
      all_project_tests_10, one_versus_all_emotion_tests_10)
  }
}
```

```{r display-1.2-results-10cutoff}
all_project_tests_10 = all_project_tests_10[!is.na(all_project_tests_10[, "p_value"]), ]
pander_clean_anova(all_project_tests_10, rename_columns=FALSE,
                   display_only_significant=TRUE)
```

```{r output_timecourse_emotion_pvalues-10cutoff}
all_project_tests_10$p_val_adjusted = p.adjust(all_project_tests_10$p_value, method="BH")
write.table(all_project_tests_10,
            file="results/models/model-timecourse-emotion-pvalues-10cutoff.tsv")
```

### Model 1.4: Do tickets and comments materially differ in gratitude over time?

#### Robustness Model 1.4: 10-contribution cutoff

```{r gratitude_modeling_per_year-10cutoff}
sentiment_frame_10$year = as.factor(sentiment_frame_10$year)
timecourse_grateful_counts = lmer(
  log(grateful_count + 1) ~ 0 + project:type:author_group:year + (1 | author_name),
  data=sentiment_frame_10,
  REML=FALSE)
```

```{r clean-up_model-1:4-output-10cutoff}
coefficients_and_se_10 = data.frame(
  summary(timecourse_grateful_counts)$coefficients)

row_names = gsub(
  "project", "", gsub(
    "author_group", "", gsub(
      "type", "", row.names(coefficients_and_se_10))))

row_names = gsub(
  "year", "", row_names)

# replace hyphens in project names with periods
row_names = gsub(
  "scikit-", "scikit.", gsub(
    "sphinx-", "sphinx.", row_names))

# convert model estimates to a dataframe
means = coefficients_and_se_10$Estimate
names(means) = row_names

# convert standard error to dataframe
se = coefficients_and_se_10$Std..Error
names(se) = row_names
```

```{r saving_results-model-1.4-10cutoff}
dir.create("results/models", showWarnings=FALSE)
write.table(coefficients_and_se_10,
            file="results/models/model-1.4-10cutoff.tsv",
            sep="\t")

```

#### Robustness Model 1.4 across projects: 10-contribution cutoff

```{r grateful-counts-all-vs-one-timecourse-10cutoff}

all_project_tests_10 = NA
all_projects = unique(sentiment_frame_10$project)

# We're going to fit the model for each projects, and concatenate the results
# in a dataframe. Then, we'll apply multiple correction and display the
# results
for(project in all_projects){
  sentiment_frame_10$test_group = sentiment_frame_10$project == project
  one_versus_all_emotion = lmer(
    log(grateful_count + 1) ~ 0 + type:author_group:test_group:year + (1|author_name),
    data=sentiment_frame_10,
    REML=FALSE)
  
  # Clean up mode
  coefficients_and_se_10 = data.frame(
    summary(one_versus_all_emotion)$coefficients)
  row_names = gsub(
    "author_group", "", 
    gsub("type", "",
         gsub("project", "", row.names(coefficients_and_se_10))))
  
  means = coefficients_and_se_10$Estimate
  names(means) = row_names
  se = coefficients_and_se_10$Std..Error
  names(se) = row_names
  
  template_contrasts = c(
    "issue_post:member:test_groupTRUE-issue_post:member:test_groupFALSE",
    "pr_post:member:test_groupTRUE-pr_post:member:test_groupFALSE",
    "issue_reply:member:test_groupTRUE-issue_reply:member:test_groupFALSE",
    "pr_reply:member:test_groupTRUE-pr_reply:member:test_groupFALSE",
    "issue_post:nonmember:test_groupTRUE-issue_post:nonmember:test_groupFALSE",
    "pr_post:nonmember:test_groupTRUE-pr_post:nonmember:test_groupFALSE",
    "issue_reply:nonmember:test_groupTRUE-issue_reply:nonmember:test_groupFALSE",
    "pr_reply:nonmember:test_groupTRUE-pr_reply:nonmember:test_groupFALSE"
  )
  
  # Now, extend this to all years.
  contrasts = c(
    unlist(
      lapply(gsub("-", ":year2009-", template_contrasts),
             function(x) paste(x, ":year2009", sep=""))),
    unlist(
      lapply(gsub("-", ":year2010-", template_contrasts),
             function(x) paste(x, ":year2010", sep=""))),
    unlist(
      lapply(gsub("-", ":year2011-", template_contrasts),
             function(x) paste(x, ":year2011", sep=""))),
    unlist(
      lapply(gsub("-", ":year2012-", template_contrasts),
             function(x) paste(x, ":year2012", sep=""))),
    unlist(
      lapply(gsub("-", ":year2013-", template_contrasts),
             function(x) paste(x, ":year2013", sep=""))),
    unlist(
      lapply(gsub("-", ":year2014-", template_contrasts),
             function(x) paste(x, ":year2014", sep=""))),
    unlist(
      lapply(gsub("-", ":year2015-", template_contrasts),
             function(x) paste(x, ":year2015", sep=""))),
    unlist(
      lapply(gsub("-", ":year2016-", template_contrasts),
             function(x) paste(x, ":year2016", sep=""))),
    unlist(
      lapply(gsub("-", ":year20110-", template_contrasts),
             function(x) paste(x, ":year2017", sep=""))),
    unlist(
      lapply(gsub("-", ":year2018-", template_contrasts),
             function(x) paste(x, ":year2018", sep=""))))
  
  
  one_versus_all_emotion_tests_10 = compute_t_statistics(
    means, se,
    contrasts)
  one_versus_all_emotion_tests_10[, "p_value"] = compute_p_value_from_t_stats(
    one_versus_all_emotion_tests_10$t_stats)
  
  # Add unique identifier based on the project of interest in the table.
  row.names(one_versus_all_emotion_tests_10) = gsub(
    "test_group", project,
    row.names(one_versus_all_emotion_tests_10))
  
  if(is.null(dim(all_project_tests_10))){
    all_project_tests_10 = one_versus_all_emotion_tests_10
  }else{
    all_project_tests_10 = rbind(
      all_project_tests_10, one_versus_all_emotion_tests_10)
  }
}
```

```{r display-gratitude-results-10cutoff}
all_project_tests_10 = all_project_tests_10[!is.na(all_project_tests_10[, "p_value"]), ]
pander_clean_anova(all_project_tests_10, rename_columns=FALSE,
                   display_only_significant=TRUE)
```

```{r gratitute_write_results-10cutoff}
all_project_tests_10$p_val_adjusted = p.adjust(all_project_tests_10$p_value, method="BH")
write.table(all_project_tests_10,
            file="results/models/model-timecourse-gratitude-pvalues-10cutoff.tsv")

